The title of the thesis:\todo{Required}

### 2020-01-21 manuscript-encoding-backup.tex
update

%THE TABLE OF CONTENTS IS TITLE CONTENTS
\addto\captionscatalan
  {\renewcommand{\contentsname}{\Large \sffamily Sumari}}

%ADD YOUR DATA
\title{The title of the thesis:Required}
\subtitle{The subtitle of the thesis: Required}
\author{Author: Required}
\thyear{of the thesis: Required}
\department{Required}
\supervisor{Required}

@@

\noindent Write here your dedication

@@

%%%%%% Thanks
\noindent {\Large \sffamily Thanks} thanks to....

@@

%ABSTRACT IN TWO LEGUAGES.
\selectlanguage{english}
\section*{\Large \sffamily Abstract}
This is the abstract of the thesis in English.  Please, use less
than 150 words.

\selectlanguage{catalan}
\vspace*{\fill}
\section*{\Large \sffamily  Resum}
Vet aquí el resum de la tesi en català.  Si us plau, utilitzeu
menys de 150 paraules.
\vspace*{\fill}

@@

%PREFACE. 
{\bf Preface}

@@

It is advisable to use the index with entries like the following, which refers to the inventor of \LaTeX:  \verb+\index{Lamport}+ \index{Lamport}. 
\begin{enumerate}
\item The orders \verb+\usepackage{makeidx} \makeindex+ in the preamble of the document and \verb+\printindex+ In the place where we want the references to appear, they cause the index to be generated. To generate it effectively you must use the program \verb+makeindex+ (it is done in a different way according to the distribution and the editor we use).
\end{enumerate}

\section*{The bibliography}
In order to be able to efficiently use bibliographic references, it is convenient to use the BibTeX program. To do it 
%\begin{enumerate}
%\item We write in the preamble \verb+\bibliographystyle{plain}+ where instead of \verb+plain+ It can be some of the usual styles, for example \verb+vancouver+\ldots Vancouver style is also included \verb+vancouver+.
%
%\item On the site of the document where we want the list of references to appear, we write \verb+ \bibliography{tesi_upf_bib}
%
%
%\end{enumerate}

@@

\todo{THIS IS MY TODO}.

@@

%NUMBER OF THE EXTERNAL PAGE EXCEPT IN THE FIRST PAGE OF EACH CAPITAL
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot{}
\fancyfoot[RO]{\thepage}
\fancyfoot[LE]{\thepage}

%MULTIPLE INDEX
%In the preamble
\usepackage{multind}
\makeindex{authors}
%Introduction to form entries
\index{authors}{Einstein}
%Situation of the Index
\printindex{authors}{Author index}
%The \ usepakage {makeidx} \ makeindex \ printindex commands must be removed
%You need to exacute from the command line makeindex authors

>>>>

%THE TABLE OF CONTENTS IS TITLE CONTENTS
%\addto\captionscatalan
  {\renewcommand{\contentsname}{\Large \sffamily Contents}}

%ADD YOUR DATA
\title{The title of the thesis:\todo{Required}}
\subtitle{The subtitle of the thesis: \todo{Required}}
\author{Author: Andrés Pérez López}
\thyear{2020}
\department{of Information and Communication Technologies}
\supervisor{}
\supervisor{Dr. Emilia Gómez Gutiérrez\\Dr. Adan Garriga Torres}

@@

\noindent Write here your dedication \todo{dedication}

@@

%%%%%% Thanks
\noindent {\Large \sffamily Thanks} thanks to....  \todo{thanks}

@@

%ABSTRACT IN TWO LEGUAGES.
\selectlanguage{english}
\section*{\Large \sffamily Abstract}
This is the abstract of the thesis in English.  Please, use less
than 150 words. \todo{abstract in english}

\selectlanguage{catalan}
\vspace*{\fill}
\section*{\Large \sffamily  Resum}
Vet aquí el resum de la tesi en català.  Si us plau, utilitzeu
menys de 150 paraules. \todo{abstract in catalan}
\vspace*{\fill}

@@

%PREFACE. 
{\bf Preface \todo{is that really needed?}}

@@

blablabla

\section*{The bibliography}
In order to be able to efficiently use bibliographic references, it is convenient to use the BibTeX program. To do it \cite{sartre1984ser}.
%\begin{enumerate}
%\item We write in the preamble \verb+\bibliographystyle{plain}+ where instead of \verb+plain+ It can be some of the usual styles, for example \verb+vancouver+\ldots Vancouver style is also included \verb+vancouver+.
%
%\item On the site of the document where we want the list of references to appear, we write \verb+ \bibliography{tesi_upf_bib}
%
%
%\end{enumerate}

@@

@@

%NUMBER OF THE EXTERNAL PAGE EXCEPT IN THE FIRST PAGE OF EACH CAPITAL
%\usepackage{fancyhdr}
%\pagestyle{fancy}
%\fancyfoot{}
%\fancyfoot[RO]{\thepage}
%\fancyfoot[LE]{\thepage}
%
%
%%MULTIPLE INDEX
%%In the preamble
%\usepackage{multind}
%\makeindex{authors}
%%Introduction to form entries
%\index{authors}{Einstein}
%%Situation of the Index
%\printindex{authors}{Author index}
%%The \ usepakage {makeidx} \ makeindex \ printindex commands must be removed
%%You need to exacute from the command line makeindex authors
